---
title: "Riddler - Rulers"
author: "Gareth Lawson"
date: "25 August 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

## Intro

This riddle comes from the Riddler at fivethirtyeight:
<https://fivethirtyeight.com/features/are-you-hip-enough-to-be-square/>

The Riddler Manufacturing Company makes all sorts of mathematical tools: compasses, protractors, slide rules - you name it!

Recently, there was an issue with the production of foot-long rulers. It seems that each ruler was accidentally sliced at three random points along the ruler, resulting in four pieces. Looking on the bright side, that means there are now four times as many rulers - they just happen to have different lengths.

On average, how long are the pieces that contain the 6-inch mark?

# Simulate cutting up one million rulers

Cutting up the rulers

```{r cars}
rulers = 100000
cuts = 3

  cut_df = tibble(r_id = rep(1:rulers, each = cuts),
         cut = runif(rulers * cuts)) %>%
    bind_rows(
      tibble(r_id = 1:rulers,
             cut = rep(1, rulers))) %>%
    arrange(r_id,cut) %>%
    group_by(r_id) %>%  
    mutate(start = lag(cut,1,0),
           length = cut - start)

```

Display the lengths of all segments (4 per ruler)

```{r}
  cut_df %>%
    ggplot(aes(length * 12)) +
    geom_histogram(
        binwidth = 0.5, 
        boundary = 1, 
        fill = 'darkgreen') +
    labs(title = "Lengths of all ruler segments",
         x = "Length (inches)",
         y = "Count") +
  theme(text = element_text(colour = 'white'),
        axis.text = element_text(colour = 'white'),
        panel.background = element_rect(fill = "transparent",colour = NA))


```

Display the lengths of the pieces of ruler that have the six inch mark

```{r}
  # segs with middle
  mids = cut_df %>%
    rowwise() %>%
    filter(cut > 0.5) %>%
    group_by(r_id) %>%  
    slice(1) %>%
    ggplot(aes(x = length * 12)) +
    geom_histogram(
      binwidth = 0.5, 
      boundary = 1, 
      fill = 'darkgreen') +
    labs(title = "Lengths of ruler segments that contain the 6 inch mark",
         x = "Length (inches)",
         y = "Count") +
  theme(text = element_text(colour = 'white'),
        axis.text = element_text(colour = 'white'),
        panel.background = element_rect(fill = "transparent",colour = NA))


```

Display the lengths of the segments that contain the various 'inch' marks

```{r}


cut_df  %>%
  rowwise() %>%
  head(10000) %>%
  crossing(mk = 0:12) %>%
  filter(cut >= mk/12) %>%
  group_by(r_id, mk) %>%  
  slice(1) %>%
  ungroup() %>%
  group_by(mk) %>%
  ggplot(aes(x = length * 12, y = mk, group = mk, fill = stat(x))) + 
  geom_density_ridges_gradient(from = 0, to = 12) +
  scale_fill_viridis_c(name = "", option = "C") +
  labs(title = "Lengths of ruler segments that contain the various inch marks",
       subtitle = "Only showing first 10000",
       x = "Length (inches)",
       y = "Inch Mark") +
  scale_y_continuous(expand = c(0, 0), breaks = seq(0,12)) +
  scale_x_continuous(expand = c(0, 0))+
  theme(text = element_text(colour = 'white'),
        axis.text = element_text(colour = 'white'),
        panel.background = element_rect(fill = "transparent",colour = NA))


  
```

