---
title: "Embracing in the Tidyverse"
author: "Gareth Lawson"
date: 2020-08-04 21:00:00 -0500 CDT
output: html_document
runtime: shiny
draft: true

---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(shiny)

```
Tidy Eval is not my strong point. 

Is it sym? or enquo? or bang bang?

Maybe we just need a nice big embrace.

<!--more-->

## Summary

Tidy Eval confuses me. 

I often have trouble referring to columns that are stored as strings. Usually after some experimenting with **!!**, **sym** and/or **enquo** I find what I'm looking for.

Recently I watched a [Hadley Wickham talk](https://www.youtube.com/watch?v=vYwXMnC03I4)  (from 18:15) that introduced me to embracing. Embracing uses double curly-brackets **{{ }}** to refer to a column.



### I have a string that I want to use as a filter

```{r, echo = FALSE}

col_1 = "cyl"

mtcars %>%
  as_tibble() %>%
  group_by( {{ col_1 }} ) %>%
  summarise(mpg = mean(mpg))



sum_by = function(col_1) {
  mtcars %>%
    as_tibble() %>%
    group_by({{col_1}}) %>%
    summarise(mpg = mean(mpg))
}

sum_by(cyl)

  

```

# References
<https://tidyeval.tidyverse.org/>
